The Key to a Data Parallel Compiler

### 2016-05-09 2016-spring-array/2016-array-key.tex
Fix tables for camera ready to fit on a single page.
More stuff for the camera ready

\documentclass[numbers,preprint]{sigplanconf}
% \usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{fontspec}
\setmainfont[Ligatures=TeX]{STIX}
\setmonofont{APL385 Unicode}
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI
\usepackage{booktabs}

@@

\conferenceinfo{ARRAY '16}{June, 2016, Santa Barbara, CA, USA}
\copyrightyear{2016}

@@

@@

For space and convenience, we use a concise array notational convention to 
describe our techniques and approach. The notation is executable and well 
established in the array community (it is a limited subset of APL). This is 
in fact the same notation used within the Co-dfns compiler itself, whose 
source code is available online and provides a complete example of the use 
of both these algorithms and this notation in the large.

All code examples are given in the following form:

@@

\begin{verbatim}
      Fd,Ft,⍪Fv
0 F f
1 E 0
2 F 0
3 E 0
4 V ⍵
4 P +
4 V ⍵
2 A 0
3 N 7
      Ed,Et,⍪Ev
0 E v
1 E 0
2 V a
2 P +
2 V b
1 P ÷
1 E 0
2 V c
2 P ×
2 V d
\end{verbatim}

@@

\bibliographystyle{plain}
\bibliography{biblio}

\begin{table}
\centering
\begin{tabular}{cll}
\toprule
Symbol                   & Monadic            & Dyadic \\
\midrule
\texttt{+}               & Identity           & Plus (Add) \\
\texttt{-}               & Negative           & Minus (Subtract) \\
\texttt{×}               & Direction (Signum) & Times (Multiply) \\
\texttt{÷}               & Reciprocal         & Divide \\
\texttt{|}               & Magnitude          & Residue (Modulo) \\
\texttt{⌊}               & Floor              & Minimum \\
\texttt{⌈}               & Ceiling            & Maximum \\
\texttt{*}               & Exponential        & Power \\
\texttt{⍟}               & Natural Logarithm  & Logarithm \\
\texttt{○}               & Pi Times           & Circular (Trigonometric) \\
\texttt{!}               & Factorial          & Binomial \\
\texttt{\textasciitilde} & Not                & \\
\texttt{?}               & Roll               & \\
\texttt{∧}              &                    & And \\
\texttt{∨}               &                    & Or \\
\texttt{⍲}               &                    & Nand \\
\texttt{⍱}               &                    & Nor \\
\texttt{<}               &                    & Less \\
\texttt{≤}               &                    & Less Or Equal \\
\texttt{=}               &                    & Equal \\
\texttt{≥}               &                    & Greater Or Equal \\
\texttt{>}               &                    & Greater \\
\texttt{≠}               &                    & Not Equal \\
\end{tabular}
\caption{Scalar Functions}
\label{tab:scalarprims}
\end{table}

\begin{table}
\centering
\begin{tabular}{cll}
\toprule
Symbol     & Monadic       & Dyadic \\
\midrule
\texttt{⍴} & Reshape       & \\
\texttt{,} & Ravel         & Catenate/Laminate \\
\texttt{⍪} & Table         & Catenate First/Laminate \\
\texttt{⌽} & Reverse       & Rotate \\
\texttt{⊖} & Reverse First & Rotate First \\
\texttt{⍉} & Transpose     & Transpose \\
\texttt{↑} & Mix           & \\
\texttt{↓} & Split         & \\
\texttt{⊂} & Enclose       & Partitioned Enclose \\
\texttt{∊} & Enlist        & \\
\end{tabular}
\caption{Structural Mixed Functions}
\label{tab:structprims}
\end{table}

\begin{table}
\centering
\begin{tabular}{cll}
\toprule
Symbol                   & Monadic  & Dyadic \\
\midrule
\texttt{⊃}               & Disclose & Pick\\
\texttt{↑}               &          & Take \\
\texttt{↓}               &          & Drop \\
\texttt{/}               &          & Replicate \\
\texttt{⌿}               &          & Replicate First \\
\texttt{\textbackslash}  &          & Expand \\
\texttt{⍀}               &          & Expand First \\
\texttt{\textasciitilde} &          & Without (Excluding) \\
\texttt{∩}               &          & Intersection \\
\texttt{∪}               & Unique   & Union \\
\texttt{⊣}               & Same     & Left \\
\texttt{⊢}               & Identity & Right\\
\end{tabular}
\caption{Selection Mixed Functions}
\label{tab:selprims}
\end{table}

\begin{table}
\centering
\begin{tabular}{cll}
\toprule
Symbol     & Monadic         & Dyadic \\
\midrule
\texttt{⍳} & Index Generator & Index Of \\
\texttt{∊} &                 & Membership \\
\texttt{⍋} & Grade Up        & Grade Up \\
\texttt{⍒} & Grade Down      & Grade Down \\
\texttt{?} &                 & Deal \\
\texttt{⍷} &                 & Find \\
\end{tabular}
\caption{Selector Mixed Functions}
\label{tab:seltorprims}
\end{table}

\begin{table}
\centering
\begin{tabular}{cll}
\toprule
Symbol     & Monadic       & Dyadic \\
\midrule
\texttt{⍴} & Shape         & \\
\texttt{≡} & Depth         & Match \\
\texttt{≢} & Tally         & Not Match \\
\texttt{⍎} & Execute       & Execute \\
\texttt{⍕} & Format        & Format \\
\texttt{⊥} &               & Decode (Base) \\
\texttt{⊤} &               & Encode (Representation) \\
\texttt{⌹} & Matrix Divide & Matrix Inverse \\
\end{tabular}
\caption{Miscellaneous Mixed Functions}
\label{tab:miscprims}
\end{table}

>>>>

\documentclass[numbers,9pt]{sigplanconf}
% \usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{fontspec}
\setmainfont[Ligatures=TeX]{STIX}
\setmonofont{APL385 Unicode}
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=false,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI
\usepackage{booktabs}

@@

\toappear{}

@@

\category{D.3.4}{Programming Languages}{Processors}[Compilers]

\keywords
APL, Parallel, Compilers, Key, Node Coordinates

@@

For space and convenience, we use a concise array notational convention to 
describe our techniques and approach. The notation is executable and well 
established in the array community (it is a limited subset of APL). This is 
in fact the same notation used within the Co-dfns compiler itself, whose 
source code is available online and provides a complete example of the use 
of both these algorithms and this notation in the large. 
All code examples are given in the following form:

@@

\begin{verbatim}
      Fd,Ft,⍪Fv  │        Ed,Et,⍪Ev
0 F f            │  0 E v
1 E 0            │  1 E 0
2 F 0            │  2 V a
3 E 0            │  2 P +
4 V ⍵            │  2 V b
4 P +            │  1 P ÷
4 V ⍵            │  1 E 0
2 A 0            │  2 V c
3 N 7            │  2 P ×
                 │  2 V d
\end{verbatim}

@@

\balancecolumns

\bibliographystyle{abbrvnat}
\bibliography{biblio}

\begin{table*}
\centering
\begin{tabular}{cllcll}
\toprule
Symbol                   & Monadic            & Dyadic  &
Symbol                   & Monadic            & Dyadic  \\
\midrule
\multicolumn{6}{c}{Scalar Functions} \\ 
\midrule
\texttt{+}               & Identity           & Plus (Add) &
\texttt{\textasciitilde} & Not                & \\
\texttt{-}               & Negative           & Minus (Subtract) &
\texttt{?}               & Roll               & \\
\texttt{×}               & Direction (Signum) & Times (Multiply) &
\texttt{∧}               &                    & And \\
\texttt{÷}               & Reciprocal         & Divide &
\texttt{∨}               &                    & Or \\
\texttt{|}               & Magnitude          & Residue (Modulo) &
\texttt{⍲}               &                    & Nand \\
\texttt{⌊}               & Floor              & Minimum &
\texttt{⍱}               &                    & Nor \\
\texttt{⌈}               & Ceiling            & Maximum &
\texttt{<}               &                    & Less \\
\texttt{*}               & Exponential        & Power &
\texttt{≤}               &                    & Less Or Equal \\
\texttt{⍟}               & Natural Logarithm  & Logarithm &
\texttt{=}               &                    & Equal \\
\texttt{○}               & Pi Times           & Circular (Trigonometric) &
\texttt{≥}               &                    & Greater Or Equal \\
\texttt{!}               & Factorial          & Binomial &
\texttt{>}               &                    & Greater \\
\texttt{≠}               &                    & Not Equal \\
\midrule
\multicolumn{3}{c}{Selection Mixed Functions} &
\multicolumn{3}{c}{Structural Mixed Functions} \\
\cmidrule(r){1-3} \cmidrule(l){4-6}
\texttt{⊃}               & Disclose & Pick &
\texttt{⍴} & Reshape       & \\
\texttt{↑}               &          & Take &
\texttt{,} & Ravel         & Catenate/Laminate \\
\texttt{↓}               &          & Drop &
\texttt{⍪} & Table         & Catenate First/Laminate \\
\texttt{/}               &          & Replicate &
\texttt{⌽} & Reverse       & Rotate \\
\texttt{⌿}               &          & Replicate First &
\texttt{⊖} & Reverse First & Rotate First \\
\texttt{\textbackslash}  &          & Expand &
\texttt{⍉} & Transpose     & Transpose \\
\texttt{⍀}               &          & Expand First &
\texttt{↑} & Mix           & \\
\texttt{\textasciitilde} &          & Without (Excluding) &
\texttt{↓} & Split         & \\
\texttt{∩}               &          & Intersection &
\texttt{⊂} & Enclose       & Partitioned Enclose \\
\texttt{∪}               & Unique   & Union &
\texttt{∊} & Enlist        & \\
\texttt{⊣}               & Same     & Left \\
\texttt{⊢}               & Identity & Right\\
\midrule
\multicolumn{3}{c}{Selector Mixed Functions} &
\multicolumn{3}{c}{Miscellaneous Mixed Functions} \\
\cmidrule(r){1-3} \cmidrule(l){4-6}
\texttt{⍳} & Index Generator & Index Of &
\texttt{⍴} & Shape         & \\
\texttt{∊} &                 & Membership &
\texttt{≡} & Depth         & Match \\
\texttt{⍋} & Grade Up        & Grade Up &
\texttt{≢} & Tally         & Not Match \\
\texttt{⍒} & Grade Down      & Grade Down &
\texttt{⍎} & Execute       & Execute \\
\texttt{?} &                 & Deal &
\texttt{⍕} & Format        & Format \\
\texttt{⍷} &                 & Find &
\texttt{⊥} &               & Decode (Base) \\
& & & \texttt{⊤} &               & Encode (Representation) \\
& & & \texttt{⌹} & Matrix Divide & Matrix Inverse \\
\end{tabular}
\caption{Primitive Functions}
\label{tab:scalarprims}
\end{table*}
